Reproducible and programmatic generation of neuroimaging visualisations

### 2022-04-05 manuscript.Rmd
sp

Precise controls via code over visualization settings, such as colour
schemes, legend placement and camera angles, can provide you with much
greater flexibility over visualisations. Nonetheless, part of the appeal
of GUI-based tools is that the pre-sets for such settings can provide a
useful starting point and reduce the decision burden on the user.
However, similar pre-sets are often available in the from of default
settings in most code-based packages, negating the need for the user to
manually enter each and every choice of setting required for making the
image. Most code-based tools also come with detialed documentation, or
even entire papers (cite ggseg and ciftitools) which provide examples of
figures which can be used as starting points or templates for new users.
As the popularity of code-sharing for figure increases, there will be an
cornucopia of templates that can be used as starting points for new
figures.

>>>>

Precise controls via code over visualization settings, such as colour
schemes, legend placement and camera angles, can provide you with much
greater flexibility over visualisations. Nonetheless, part of the appeal
of GUI-based tools is that the pre-sets for such settings can provide a
useful starting point and reduce the decision burden on the user.
However, similar pre-sets are often available in the form of default
settings in most code-based packages, negating the need for the user to
manually enter each and every choice of setting required for making the
image. Most code-based tools also come with detialed documentation, or
even entire papers (cite ggseg and ciftitools) which provide examples of
figures which can be used as starting points or templates for new users.
As the popularity of code-sharing for figure increases, there will be an
cornucopia of templates that can be used as starting points for new
figures.
